Triangulated categories was allegedly discovered independently by Dieter Puppe and Jean-Louis Verdier in 1962 and 1963 respectively. Verdier introduced his axioms in his doctoral thesis, supervised by the famous Alexander Groethendieck, leading to the attribution for the discovery of triangulated category sometimes being split three ways between Puppe, Verdier, and Groethendieck. Puppe discovered triangulated categories while looking at the stable homotopy category, while Verdier and Groethendieck were motivated from a more algebraic viewpoint by the derived categroy of an abelian category.

% TODO: Fix claims and references when finished.
As it's discovery would imply, triangulated categories are useful in both algebra and topology. Notable algebra inspired triangulated categories are: the derived categories of abelian category as mentioned above, the stable module category, as well as the homotopy category of chain complexes. On the other hand, notable topology inspired triangulated categories are: the stable homotopy category, and the Spanier-Whitehead category. This thesis will touch a little upon the Spanier-Whitehead category and the derived category of an abelian category in section 2, but will mainly focus on the stable module category for use in examples throughout the thesis, along with a proof that it's a triangulated category in section 2.

% MS-Question: Dwyer-Kan influence on Shipley?
Toda brackets were initially introduced by Hiroshi Toda in 1962 for use in calculating homotopy groups of spheres. In this thesis a definition of Toda brackets on any triangulated category, as was first introduced by Shipley in 2002 \cite[Definition A.2]{Shipley_2002}, based on ideas from Cohen in 1968 \cite[Definition on bottom of p. 308]{Cohen_1968} and built upon by Sagave in 2008 \cite[Remark 4.5]{Sagave_2008}. The definitions in this thesis is a more elegant formulation of Segave's definitions by Christensen and Frankland in 2017 \cite[Definition 3.1]{Christensen-Frankland_2017}.

Like Toda brackets, Massey products were originally not defined for Triangulated categories. Massey products were introduced by William Schumacher Massey in 1958. WIP


defined on triangulated categories. in order to describe the differential on the second page of the Adams spectral sequence. However, a big issue with Toda brackets is the difficulty of computing them.

Luckily, for certain triangulated categories, namely the algebraic triangulated categories, one can define Massey products. Massey products are generally easier to computa than Toda brackets, and in an algebraic triangulated category, they are almost equal, up to a potential sign difference. 
% Massey also created the exact couple method of constructing spectral sequences, which is the technique used in this thesis to define the Adams spectral sequence in section 6.

On an arbitrary triangulated category one can create an Adams spectral sequence, which is a spectral sequence introduced in 1958 by John Frank Adams for use in computing homotopy groups of spectra. It is an useful computational tool, and what makes it especially interesting for this thesis is it's connection to Toda brackets.

Therefore, by using Massey products, one can potentially calculate the page two differential of an Adams spectral sequence more efficiently than conventional methods.

% TODO: Cite Haynes Miller - Toda triang/Adams?. 
% Ikkje ver så bastant i ordbruken rundt at Toda/Massey berre er knytt til triangulerte kategoriar.
% Følg planen som Marius skreiv på tavlo.
% Kildeplagiat? Er det ei greie?

By NTNU, it is mandatory to include the following subsection.
\subsubsection{Sustainability statement}
\input{sections/1.1.1_sustainability_statement.tex}

This thesis will assume that the reader is already familiar with basic homological algebra as well as some module theory.
