To get a better understanding of how to compute Toda brackets, as well as illustrate some properties they have, this section contains four simple examples in the category \( \Mc := \StMod(R) \) where \( R := \Fb_2 C_2 \), which will serve as a warm-up for the future more complicated examples.

The following remark contains some preliminary information that is helpful in the following computations:

\begin{remark}
	\label{rem:toda_bracket_examples_properties}
    Let \( g \) denote the generator of \( C_2 \).

    The ideal \( J := \tuple{1 + g} \) is the only non-trivial ideal in \( R \) (up to isomorphism).

    The ideal \( J \) is not projective, since the short exact sequence
    \begin{center}
        \begin{tikzpicture}
            \diagram{m}{1cm}{1cm}{
                J \& R \& J, \\
            };
        
            \draw[math]
                (m-1-1) edge[hook] node {\kappa_J} (m-1-2)
                (m-1-2) edge[two heads] node {\rho_J} (m-1-3);
        \end{tikzpicture}
    \end{center}
    where \( \kappa_J \) is the inclusion and \( \rho_J \) is the morphism
    \begin{align*}
        \rho_J: R &\to J \\
        0, 1 + g &\mapsto 0 \\
        1, g &\mapsto 1 + g,
    \end{align*}
    is not split.

    This is because \( \kappa_J \) is the only monomorphism of \( J \) into \( R \), but composes to \( 0 \) with \( \rho_J \). Therefore \( J \) cannot be projective, since every epimorphism into a projective module splits.

    The supension \( \Sigma J \) is assumed to be the cokernel of \( \kappa_J \), which by the short exact sequence above, can be assumed to be \( J \).

	% Furthermore, since \( \rho_J \) is an epimorphism with kernel \( J \), one gets from the third isomorphism theorem that \( \frac{R}{J} \cong J \). Let the isomorphism from \( \frac{R}{J} \) to \( J \) also be denoted as \( \rho_J \).
\end{remark}

Here are the examples:

\begin{example}
	Let the following be a diagram in \( \Mc \)
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm}{
					J \& J \& J \& J \\
			};

			\draw[math]
				(m-1-1) edge node {[\Id_J]} (m-1-2)
				(m-1-2) edge node {[0]} (m-1-3)
				(m-1-3) edge node {[\Id_J]} (m-1-4);
		\end{tikzpicture}
	\end{center}
	the goal is to calculate the Toda bracket \( \toda{\Id_J, 0, \Id_J} \).

	Using the iterated cofiber definition of Toda bracket, then the first step is to calculate the standard triangle of \( \Id_J \). By the assumptions in \autoref{rem:toda_bracket_examples_properties}, the cone is isomorphic to \( 0 \) and the suspension of \( \Id_J \) is \( J \).

	This yields the following distinguished triangle
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \& J \& 0 \& J. \\
			};

			\draw[math]
				(m-1-1) edge node {[\Id_J]} (m-1-2)
				(m-1-2) edge node {[0]} (m-1-3)
				(m-1-3) edge node {[0]} (m-1-4);
		\end{tikzpicture}
	\end{center}

	Using the iterated cofiber definition of Toda bracket, one gets the following diagram
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \& J \& 0 \& J \\
				J \& J \& J \& J \\
			};

			\draw[math]
				(m-1-1) edge node {[\Id_J]} (m-1-2)
					edge[equal] (m-2-1)
				(m-1-2) edge node {[0]} (m-1-3)
					edge[equal] (m-2-2)
				(m-1-3) edge node {[0]} (m-1-4)
					edge node {[\rho]} (m-2-3)
				(m-1-4) edge node {[\psi]} (m-2-4)

				(m-2-1) edge node {[\Id_J]} (m-2-2)
				(m-2-2) edge node {[0]} (m-2-3)
				(m-2-3) edge node {[\Id_J]} (m-2-4);
		\end{tikzpicture}
	\end{center}

	But this shows that any endomorphism on \( J \) makes the rightmost square commute, and is therefore in the Toda bracket. In addition, since \( \Mod(R)(J, J) \) is simply \( \set{0, \Id_J} \), this implies that \( \Mc(J, J) = \set{[0], [\Id_J]} \).

	Therefore \( \toda{[\Id_J], [0], [\Id_J]} = \set{[0], [\Id_J]} \). 
\end{example}

One thing that was shown in this example, is that the Toda bracket is dependant on the choice of \( I \) in \autoref{def:stmod_sigma}. In the previous example, one could have assumed \( \Sigma J \) to be \( \frac{R}{J} \), which would have yielded the Toda bracket \( \toda{[\Id_J], [0], [\Id_J]} = \set{[0], [\rho_J]} \). Therefore for applications of Toda brackets on stable module categories, it is important to keep in mind that the choice of \( I \) in the definition of \( \Sigma \) is consistent.

\begin{example}
	\label{ex:toda_bracket-1}
	The goal is to calculate \( \toda{\Id_J, \Id_J, \Id_J} \).

	One has the following diagram by the iterated cofiber definition of toda bracket using the assumptions made in \autoref{rem:toda_bracket_examples_properties}
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \& J \& 0 \& J \\
				J \& J \& J \& J. \\
			};

			\draw[math]
				(m-1-1) edge node {[\Id_J]} (m-1-2)
					edge[equal] (m-2-1)
				(m-1-2) edge node {[0]} (m-1-3)
					edge[equal] (m-2-2)
				(m-1-3) edge node {[0]} (m-1-4)
					edge[squiggly] node {[\rho]} (m-2-3)
				(m-1-4) edge node {[\psi]} (m-2-4)

				(m-2-1) edge node {[\Id_J]} (m-2-2)
				(m-2-2) edge node {[\Id_J]} (m-2-3)
				(m-2-3) edge node {[\Id_J]} (m-2-4);
		\end{tikzpicture}
	\end{center}

	However there is an issue. There exists no \( [\rho]: 0 \to J \) such that \( [\rho] \circ [0] = [0]: J \to J \) is equal to \( [\Id_J] \). It could only be true if \( J \cong 0 \), which it is not, since \( J \) is not projective by the argument in \autoref{rem:toda_bracket_examples_properties}.

	Therefore the Toda bracket is \emph{empty}, i.e. \( \toda{\Id_J, \Id_J, \Id_J} = \emptyset \).
\end{example}

The previous example shows another important property of Toda brackets, namely that it can be empty in certain circumstances. The following proposition and proof shows this property.

\begin{proposition}
	Let \( f_1, f_2, f_3 \) be three composable morphisms in any triangulated category, \( \Tc \),
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				X_1 \& X_2 \& X_3 \& X_4 \\
			};

			\draw[math]
				(m-1-1) edge node {f_1} (m-1-2)
				(m-1-2) edge node {f_2} (m-1-3)
				(m-1-3) edge node {f_3} (m-1-4);
		\end{tikzpicture}
	\end{center}
	such that \( f_2 \circ f_1 \neq 0 \) or \( f_3 \circ f_2 \neq 0 \).

	Then \( \toda{f_3, f_2, f_1} = \emptyset \).
\end{proposition}
\begin{proof}
	Assume that \( \toda{f_3, f_2, f_1} \neq \emptyset \). Then from the iterated cofiber definition of Toda bracket there exists morphisms \( \alpha, \beta, \phi, \psi \) such that the following diagram commutes, and the top row is distinguished
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				X_1 \& X_2 \& C_{f_1} \& \Sigma X_1 \\
				X_1 \& X_2 \& X_3 \& X_4. \\
			};

			\draw[math]
				(m-1-1) edge node {f_1} (m-1-2)
					edge[equal]	(m-2-1)
				(m-1-2) edge node {\alpha} (m-1-3)
					edge[equal] (m-2-2)
				(m-1-3) edge node {\beta} (m-1-4)
					edge node {\phi} (m-2-3)
				(m-1-4) edge node {\psi} (m-2-4)

				(m-2-1) edge node {f_1} (m-2-2)
				(m-2-2) edge node {f_2} (m-2-3)
				(m-2-3) edge node {f_3} (m-2-4);
		\end{tikzpicture}
	\end{center}

	Split the proof into two different contradictions:

	\begin{itemize}
		\item{
			Case 1:

			Assume that \( f_2 \circ f_1 \neq 0 \). Then since \( \alpha, f_1 \) are two composable morphisms from the same distinguished triangle one has
			\[
				\phi \circ \alpha \circ f_1 = \phi \circ 0 = 0.
			\]

			But from commutativity of the diagram one also has
			\[
				\phi \circ \alpha \circ f_1 = f_2 \circ f_1 \neq 0.
			\]

			Which is a contradiction.
		}
		\item{
			Case 2:

			Assume that \( f_3 \circ f_2 \neq 0 \). Then one has that
			\[
				0 = \psi \circ 0 = \psi \circ \beta \circ \alpha = f_3 \circ \phi \circ \alpha = f_3 \circ f_2 \neq 0.
			\]
			Which is also a contradiction.
		}
	\end{itemize}

	Therefore both \( f_2 \circ f_1 = 0 \) and \( f_3 \circ f_2 = 0 \) if \( \toda{f_3, f_2, f_1} \neq \emptyset \), which is contrapositive to the statement in the theorem.
\end{proof}

The following example is a generalization of \autoref{ex:toda_bracket-1} on any triangulated category \( \Tc \).

\begin{example}
	The goal is to compute \( \toda{f, 0, \Id} \) for any triangulated category \( \Tc \) and for any \( f \in \Tc(X_2, X_3) \).

	First note that on any triangulated category, the cone of the identity morphism is isomorphic to \( 0 \). Then using the iterated cofiber definition of Toda brackets, one gets the following diagram
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				X_1 \& X_1 \& 0 \& \Sigma X_1 \\
				X_1 \& X_1 \& X_2 \& X_3. \\
			};

			\draw[math]
				(m-1-1) edge node {\Id} (m-1-2)
					edge[equal] (m-2-1)
				(m-1-2) edge (m-1-3)
					edge[equal] (m-2-2)
				(m-1-3) edge (m-1-4)
					edge (m-2-3)
				(m-1-4) edge node {\psi} (m-2-4)

				(m-2-1) edge node {\Id} (m-2-2)
				(m-2-2) edge node {0} (m-2-3)
				(m-2-3) edge node {f} (m-2-4);
		\end{tikzpicture}
	\end{center}

	Here one has that any possible \( \psi: \Sigma X_1 \to X_3 \) will make the right square commute. Therefore \( \toda{f_3, 0, \Id} = \Tc(\Sigma X_1, X_3) \).
\end{example}

Finally, the last example will be in \( \Mc \), but a little more complicated computation.

\begin{example}
	The goal is to compute the Toda bracket of the following morphisms using the cofiber-cofiber definition,
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \& {J \oplus J} \& {J \oplus J} \& J. \\
			};

			\draw[math]
				(m-1-1) edge node {\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}} (m-1-2)
				(m-1-2) edge node {\begin{psmallmatrix} 1 & 1 \\ 1 & 1 \end{psmallmatrix}} (m-1-3)
				(m-1-3) edge node {\begin{psmallmatrix} 1 & 1 \end{psmallmatrix}} (m-1-4);
		\end{tikzpicture}
	\end{center}

	First find the standard triangle of \( \begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}: J \to J \oplus J \).

	The cone is defined as the pushout of the following diagram,
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \& J \oplus J \\
				R, \\
			};

			\draw[math]
				(m-1-1) edge node {\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}} (m-1-2)
					edge[hook] node[swap] {\kappa_J} (m-2-1);
		\end{tikzpicture}
	\end{center}
	where \( \kappa_J \) is assumed to be as in \autoref{rem:toda_bracket_examples_properties}.

	In the category of \( \Mod(R) \), the pushout becomes
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \& J \oplus J \\
				R \& \frac{J \oplus J \oplus R}{\sim}, \\
			};

			\draw[math]
				(m-1-1) edge node {\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}} (m-1-2)
					edge[hook] node[swap] {\kappa_J} (m-2-1)
				(m-1-2) edge[hook] node {\rho} (m-2-2)

				(m-2-1) edge node {\gamma} (m-2-2);
		\end{tikzpicture}
	\end{center}
	where \( (1 + g, 1 + g, 0) \sim (0, 0, 1 + g) \).

	The morphism \( \rho \) is given as the composition
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \oplus J \& J \oplus J \oplus R \& \frac{J \oplus J \oplus R}{\sim} \\
			};

			\draw[math]
				(m-1-1) edge[hook] node {i} (m-1-2)
				(m-1-2) edge[two heads] node {\pi} (m-1-3);
		\end{tikzpicture}
	\end{center}
	where \( i \) is the embedding, and \( \pi \) is the quotient epimorphism.

	One can check that the cone is isomorphic to \( J \oplus R \) via the morphism
	\begin{align*}
		\alpha: \frac{J \oplus J \oplus R}{\sim} &\to J \oplus R \\
		(0, 0, r) &\mapsto (0, r) \\
		(1 + g, 0, r) &\mapsto (1 + g, r + 1 + g) \\
		(0, 1 + g, r) &\mapsto (1 + g, r) \\
		(1 + g, 1 + g, r) &\mapsto (0, r + 1 + g). \\
	\end{align*}

	Therefore, by checking the morphism \( \alpha \circ \rho \) one can see that it becomes
	\[
		\begin{psmallmatrix}
			1 & 1 \\
			\kappa_J & 0 \\
		\end{psmallmatrix}:  J \oplus J \to J \oplus R.
	\]

	Doing a similar argument for \( \gamma \), one gets that it is simply the embedding into \( J \oplus R \), here denoted as \( \begin{psmallmatrix} 0 \\ 1 \\ \end{psmallmatrix} \).

	Thus, one can rewrite the pushout to the form
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \& J \oplus J \\
				R \& J \oplus R \\
			};

			\draw[math]
				(m-1-1) edge node {\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}} (m-1-2)
					edge[hook] node[swap] {\kappa_J} (m-2-1)
				(m-1-2) edge[hook] node {\begin{psmallmatrix} 1 & 1 \\ \kappa_J & 0 \\ \end{psmallmatrix}} (m-2-2)

				(m-2-1) edge node {\begin{psmallmatrix} 0 \\ 1 \\ \end{psmallmatrix}} (m-2-2);
		\end{tikzpicture}
	\end{center}
	
	Furthermore, the map \( J \oplus R \to \Sigma J = J \) is given as the unique pushout map \( \beta \), satisfying the following commutative diagram
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \& J \oplus J \\
				R \& J \oplus R \\
				\& J \\
			};

			\draw[math]
				(m-1-1) edge node {\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}} (m-1-2)
					edge[hook] node[swap] {\kappa_J} (m-2-1)
				(m-1-2) edge node[swap] {\begin{psmallmatrix} 1 & 1 \\ \kappa_J & 0 \\ \end{psmallmatrix}} (m-2-2)
					edge[curve={height=-25pt}] node {0} (m-3-2) 

				(m-2-1) edge[hook] node {\begin{psmallmatrix} 0 \\ 1 \\ \end{psmallmatrix}} (m-2-2)
					edge node {\rho_J} (m-3-2)
				(m-2-2) edge node {\beta} (m-3-2);
		\end{tikzpicture}
	\end{center}

	One can check that a candidate for the map \( \beta \) is \( \begin{psmallmatrix} 0 & \rho_J \\ \end{psmallmatrix} \). And since \( \beta \) is unique, this is the only map making the diagram commute.

	Therefore the standard triangle becomes
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{2cm} {
				J \& J \oplus J \& J \oplus R \& J. \\
			};

			\draw[math]
				(m-1-1) edge node {\class{\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}}} (m-1-2)
				(m-1-2) edge node {\class{\begin{psmallmatrix} 1 & 1 \\ \kappa_J & 0 \\ \end{psmallmatrix}}} (m-1-3)
				(m-1-3) edge node {\class{\begin{psmallmatrix} 0 & \rho_J \\ \end{psmallmatrix}}} (m-1-4);
		\end{tikzpicture}
	\end{center}

	In \( \Mc \), \( R \cong 0 \), and the morphism \( \begin{psmallmatrix} 1 & 0 \\ \end{psmallmatrix}: J \oplus R \to J \) becomes an isomorphism which yields the following distinguished triangle
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{2cm} {
				J \& J \oplus J \& J \& J. \\
			};

			\draw[math]
				(m-1-1) edge node {\class{\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}}} (m-1-2)
				(m-1-2) edge node {\class{\begin{psmallmatrix} 1 & 1 \\ \end{psmallmatrix}}} (m-1-3)
				(m-1-3) edge node {0} (m-1-4);
		\end{tikzpicture}
	\end{center}

	Using the cofiber-cofiber definition of Toda bracket, one gets the following commutative diagram
	\begin{center}
		\begin{tikzpicture}
			\diagram{m}{1cm}{1cm} {
				J \& {J \oplus J} \& J \& J \\
				J \& {J \oplus J} \& {J \oplus J} \& J, \\
			};

			\draw[math]
				(m-1-1) edge node {\class{\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}}} (m-1-2)
					edge[equal] (m-2-1)
				(m-1-2) edge node {\class{\begin{psmallmatrix} 1 & 1 \\ \end{psmallmatrix}}} (m-1-3)
					edge[equal] (m-2-2)
				(m-1-3) edge node {[0]} (m-1-4)
					edge node {\phi} (m-2-3)
				(m-1-4) edge node {\psi} (m-2-4)

				(m-2-1) edge node {\class{\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}}} (m-2-2)
				(m-2-2) edge node {\class{\begin{psmallmatrix} 1 & 1 \\ 1 & 1 \end{psmallmatrix}}} (m-2-3)
				(m-2-3) edge node {\class{\begin{psmallmatrix} 1 & 1 \end{psmallmatrix}}} (m-2-4);
		\end{tikzpicture}
	\end{center}
	where the top row is distinguished.

	Now, one has to find every possible \( \psi \) such that the above diagram commutes for some \( \phi \).

	Start by assuming
	\[ 
		\phi = \class{
			\begin{psmallmatrix}
				1 \\
				1
			\end{psmallmatrix}
		},
	\]
	this makes the square to the left of \( \phi \) commute, in addition, it makes the square to the right of \( \phi \) also commute, because
	\[
		\class{\begin{psmallmatrix} 1 & 1 \end{psmallmatrix}} \circ
		\begin{psmallmatrix}
			1 \\
			1
		\end{psmallmatrix}
		=
		[2] = [0].
	\]

	Thus, with the assumed \( \phi \), any \( \psi \) will make the diagram commute. Therefore
	\[ 
		\toda{\class{\begin{psmallmatrix} 1 & 1 \end{psmallmatrix}}, \class{\begin{psmallmatrix} 1 & 1 \\ 1 & 1 \end{psmallmatrix}}, \class{\begin{psmallmatrix} 1 \\ 1 \end{psmallmatrix}}} = \Mc(J, J).
	\]
\end{example}

If at the end of the final example one wasn't so lucky and couldn't have chosen a \( \phi \), such that every \( \psi \) was expressed, the calculations would have become much more tedious. Then one would have to find every possible \( \phi \), and from every possible \( \phi \) one would then find every possible \( \psi \). In addition, working with morphisms in \( \Mc \) is not simple, and one could end up with a very complicated and annoying calculation. Combining this with the fact that simply calculating an appropriate distinguished triangle was tedious, and the calculations become even worse.

This illustrates the reason for wanting to combine Massye products and Toda brackets as mentioned in \autoref{subsection:1.1-Motivation}. If Massey products are easier to compute than Toda brackets, then that would help a lot in doing more complicated computations.
