The following lemma, is essential in the definition of Massey products on \( H^0(\dgM) \) and therefore any algebraic triangulated category, which will become apparent later on.

\begin{lemma}
    \label{cor:H^i_dgmod_cong_H^0_with_shift}
    Let \( F, G \in \dgM \).

    Then there is a canonical isomorphism
    \begin{align*}
        H^0(\phi): H^i(\dgM(F, G)) &\to H^0(\dgM)(\Sigma^{-i} F, G) \\
        \eta &\mapsto \eta.
    \end{align*}
\end{lemma}
\begin{proof}
    Apply \( H^0 \) to \( \phi \) in \autoref{lem:dgmod_shift_eq_plus}.
\end{proof}

Using the above lemma, we define how to take the Massey product in \( H^0(\dgM) \) as follows.

\begin{definition}[Massey product on \( H^0(\dgM) \)]
    \label{def:massey_product_H^0(dgMod_dg(C))}
    Let \( \Cc \) be a small DG-category.
    
    Let the following be a diagram in \( H^0(\dgM) \)
    \begin{center}
        \begin{tikzpicture}
            \diagram{m}{1cm}{1cm} {
                X_1 \& X_2 \& X_3 \& X_4. \\
            };

            \draw[math]
                (m-1-1) edge node {f_1} (m-1-2)
                (m-1-2) edge node {f_2} (m-1-3)
                (m-1-3) edge node {f_3} (m-1-4);
        \end{tikzpicture}
    \end{center}
    Considering this as a DG-diagram in \( H^{\bullet}(\dgM) \), with \( |f_i| = 0 \), and the canonical isomorphism from \autoref{cor:H^i_dgmod_cong_H^0_with_shift}, let the following
    \[
        \massey{f_3, f_2, f_1} \subseteq H^0(\dgM)(\Sigma X_1, X_4)
    \]
    be called the \emph{Massey product of \( f_1, f_2, f_3 \) in \( H^0(\dgM) \)}.
\end{definition}

Using the above definition, we can define the Massey product more generally in an algebraic triangulated category.

\begin{definition}[Massey product in an algebraic triangulated category]
    \label{def:massey_product_alg_tri_cat}
    Let \( \Tc \) be an algebraic triangulated category and let \( \Cc \) be a DG-enhancement of \( \Tc \) with \( \Phi: \Tc \to H^0(\Cc) \) an equivalence by the algebraic triangulated category property. Suppose \( \phi: \Phi^{-1} H^0(\mathbf{h})^{-1} H^0(\mathbf{h}) \Phi \to \Id_{\Tc} \) be a natural isomorphism arising from the fact that \( H^0(\mathbf{h}) \Phi \) is an equivalence. Furthermore, let \( \eta: H^0(\mathbf{h}) \Phi \Sigma \to \Sigma H^0(\mathbf{h}) \Phi \) be a natural isomorphism from the fact that \( H^0(\mathbf{h}) \Phi \) is a triangulated functor onto its image.
    
    Let the following be a diagram in \( \Tc \)
    \begin{center}
        \begin{tikzpicture}
            \diagram{m}{1cm}{1cm} {
                X_1 \& X_2 \& X_3 \& X_4. \\
            };

            \draw[math]
                (m-1-1) edge node {f_1} (m-1-2)
                (m-1-2) edge node {f_2} (m-1-3)
                (m-1-3) edge node {f_3} (m-1-4);
        \end{tikzpicture}
    \end{center}
    Consider again the following diagram in \( \im(H^0(\mathbf{h}) \Phi) \),
    \begin{center}
        \begin{tikzpicture}
            \diagram{m}{1cm}{1cm} {
                H^0(\mathbf{h}) \Phi X_1 \& H^0(\mathbf{h}) \Phi X_2 \& H^0(\mathbf{h}) \Phi X_3 \& H^0(\mathbf{h}) \Phi X_4 \\
            };

            \draw[math]
                (m-1-1) edge node {H^0(\mathbf{h}) \Phi f_1} (m-1-2)
                (m-1-2) edge node {H^0(\mathbf{h}) \Phi f_2} (m-1-3)
                (m-1-3) edge node {H^0(\mathbf{h}) \Phi f_3} (m-1-4);
        \end{tikzpicture}
    \end{center}
    and take the Massey product of the above diagram in \( H^0(\dgM) \) to get
    \[
        \massey{H^0(\mathbf{h}) \Phi f_3, H^0(\mathbf{h}) \Phi f_2, H^0(\mathbf{h}) \Phi f_1} \subseteq H^0(\dgM)(\Sigma H^0(\mathbf{h}) \Phi X_1, H^0(\mathbf{h}) \Phi X_4).
    \]
    Then pre-compose with \( \eta_{X_1} \) and apply \( \Phi^{-1} H^0(\mathbf{h})^{-1} \) to get
    \[
        \Phi^{-1} H^0(\mathbf{h})^{-1} (\massey{H^0(\mathbf{h}) \Phi f_3, H^0(\mathbf{h}) \Phi f_2, H^0(\mathbf{h}) \Phi f_1} \circ \eta_{X_1}),
    \]
    which, up to pre- and post-composition with \( \phi \), yields
    \[
        \phi_{X_4} \circ \tuple*{\Phi^{-1} H^0(\mathbf{h})^{-1} (\massey{H^0(\mathbf{h}) \Phi f_3, H^0(\mathbf{h}) \Phi f_2, H^0(\mathbf{h}) \Phi f_1} \circ \eta_{X_1})} \circ \phi^{-1}_{\Sigma X_1} \subseteq \Tc(\Sigma X_1, X_4).
    \]

    This subset of \( \Tc(\Sigma X_1, X_4) \) is called the \emph{Massey product of \( f_1, f_2 \) and \( f_3 \) in an algebraic triangulated category}.
\end{definition}

The above definition is well-defined since \( \im(H^0(\mathbf{h}) \Phi) \) is a full and triangulated subcategory of \( H^0(\dgM) \), and so Massey products is well-defined on \( \im(H^0(\mathbf{h}) \Phi) \) since
\begin{align*}
    H^0(\dgM)(\Sigma H^0(\mathbf{h}) \Phi X_1, H^0(\mathbf{h}) \Phi X_4) \circ \eta_{X_1} = \im(H^0(\mathbf{h}) \Phi)(H^0(\mathbf{h}) \Phi \Sigma X_1, H^0(\mathbf{h}) \Phi X_4).
\end{align*}

It is not obvious why different choices of DG-enhancements would yield the same Massey product in an algebraic triangulated category. However, this turns out to not be an issue, as this follows from the proof of our main result, \autoref{theorem:massey_equals_toda}, since they would all be equal to the same Toda bracket.