\begin{notation}
    Let \( \Cc \) be any additive category.
    
    Then let \( \C \tuple{\Cc} \) denote the category of chain complexes of objects in \( \Cc \).

    Furthermore let the differential in these chain complexes have \emph{ascending} order, i.e., for \( M_i, M_{i+1} \in \Cc \) which are adjacent objects in a chain complex \( M \in \C \tuple{\Cc} \), the differential would be
    \[
        d_i : M_i \to M_{i + 1}.
    \]
\end{notation}

% TODO: Obvious?
\begin{notation}
    In this section, there will be a lot of products and coproducts of modules mentioned, and so a small note on the notation of elements, and the reasoning behind the notation could be useful.

    Let \( R \) be a commutative ring with identity. Let \( A_i \in \Mod(R) \) and let
    \[
        \iota_i: A_i \to \coprod_{i \in \Zb} A_i
    \]
    denote the canonical split monomorphism by the universal property of the coproduct in \( \Mod(R) \).

    Then for any \( a_i \in A_i \), the element
    \[
        \iota_i(a_i) \in \coprod_{i \in \Zb} A_i
    \]
    is just denoted as
    \[
        a_i \in \coprod_{i \in \Zb} A_i.
    \]
    
    The reasoning for the above notation is twofold. Firstly, it reduces notation while not being ambigous. Secondly, one never talks about a general element of a coproduct. Almost always when talking about what a morphism does to an element of the coproduct, it is what happens to the \( \iota_i(a_i) \)'s, which is a consequence of the universal property of the coproduct.

    In addition, let 
    \[
        \pi_i: \prod_{i \in \Zb} A_i \to A_i
    \]
    be the universal split epimorphism by the universal property of the product in \( \Mod(R) \).
    
    Then for any element \( a \in \prod_{i \in \Zb} A_i \), denote
    \[
        a = \tuple{a_i}_{i \in \Zb} \in \prod_{i \in \Zb} A_i
    \]
    where \( a_i := \pi_i(a) \in A_i \).
    
    The reasoning behind this notation is because the product in \( \Mod(R) \) is the direct product, and because the universal property of the product. That is because it makes it so that when talking about morphisms into the product, the morphism is fully defined by what it does to each degree in \( \prod_{i \in \Zb} A_i \), which is easily shown using the above notation.  
\end{notation}

% Section wide TODO's: Unit morphism in enriched category, notation for elements in a coproduct.

\subsection{Definition of a DG-category}
\input{sections/massey_product_in_dg_cat/definition_of_dg-category.tex}

\subsection{Definition of Massey Product in a DG-category}
\input{sections/massey_product_in_dg_cat/massey_product_definition.tex}

\subsection{What is a pre-triangulated category?}
\input{sections/massey_product_in_dg_cat/what_is_a_pre-triangulated_cat.tex}

\subsection{Why do Massey product and toda brackets intersect?}
\input{sections/massey_product_in_dg_cat/massey_v_toda.tex}
